Investigating Police Citations in Houston

### 2023-04-17 Final Presentation.Rmd
update

---
title: "Final Presenation"
author: "Siddhi Narayan, Grace Wang, Virginia"
date: "2023-04-17"
output: 
  ioslides_presentation:
    widescreen: true
    css: style.css
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 12, fig.height = 8, out.width = "100%")
```

@@

## Citation by Race
* How close is this to the truth?
```{r Waffle, message=FALSE}
source("subscripts/waffle.R", local=TRUE, print.eval=TRUE)
waffle()
```

@@

## Killer Plot
* Further breakdown Killer Plot by Police District
<iframe src="http://127.0.0.1:5771" width="100%" height="500px"></iframe>

>>>>

---
title: "Final Presenation"
author: "Siddhi Narayan, Grace Wang, Virginia"
date: "2023-04-17"
output: 
  ioslides_presentation:
    widescreen: true
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 10, fig.height = 6, out.width = "100%")
```

@@

## Citation by Race 
```{r Waffle, message=FALSE}
source("subscripts/waffle.R", local=TRUE, print.eval=TRUE)
waffle()
```

@@

## Killer Plot
<iframe src="http://127.0.0.1:5290" width="100%" height="500px"></iframe>

### 2023-04-17 draft4.Rmd
update push
update

legend("topright", legend=c("black", "white", "aapi", "unknown", "other"), col=c("blue", "red", "green", "orange", "purple"), pch = 20, cex = 0.7, title = "Race")

@@

plot(mini_htx2$lat, mini_htx2$lng, col = mini_htx2$district, panel.first = grid(8,8),  xlim = c(29.5, 30.15), ylim = c(-96, -95), main = "Latitude & Longitude of Stops by District", xlab = "Latitude", ylab = "Longitude", pch=1)
legend("bottomright", legend=levels(mini_htx2$district), cex = 0.62, pch=1, col=unique(mini_htx2$district), title = "District")
```

>>>>

graphics::legend("topright", 
       legend=c("black", "white", "aapi", "unknown", "other"), 
       col=c("blue", "red", "green", "orange", "purple"), 
       pch = 20, cex = 0.7, title = "Race")

@@

plot(mini_htx2$lat, mini_htx2$lng, col = mini_htx2$district, panel.first = grid(8,8),  xlim = c(29.5, 30.15), ylim = c(-96, -95), main = "Latitude & Longitude of Stops by District", xlab = "Latitude", ylab = "Longitude", pch=1)
graphics::legend("bottomright", legend=levels(mini_htx2$district), cex = 0.62, pch=1, col=unique(mini_htx2$district), title = "District")
```
